Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-24 WSSSPE2_report/WSSSPE2_review.tex
Added TODOs
minor cleanup of affiliations
modify description of notes URLs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Lead: Choi. Volunteers welcome---contact lead.  See \url{http://tinyurl.com/q6ew45v}}
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Kaitlin Thaney, Designing for Truth, Scale, and Sustainability}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Neil }
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

google doc notes - \url{http://tinyurl.com/kqpe87z}
%https://docs.google.com/document/d/1Mivadj16_9tPrw8Nxmhp72AtNC0BEVO-f7M84FXTbSU/edit#heading=h.elaktnt2tep9

@@

google notes doc - 
\url{http://tinyurl.com/l5t5h45}
%https://docs.google.com/document/d/1G1_U5-hkAvDKtTgT4DvUhIYvyYUY4cBBvQHJIdgADa0/edit#heading=h.v7g0nqpn1fur

@@

{\small
\begin{longtable}{ll}
   Jordan Adams          &  Tulane University                                                                    
\\ Alice Allen           &  Astrophysics Source Code Library (ASCL)                                              
\\ Gabrielle Allen       &  U Illinois                                                                           
\\ Pierre-Yves Aquilanti &  TOTAL E\&P R\&T USA                                                                  
\\ Wolfgang Bangerth     
\\ David Bernholdt       &  Oak Ridge National Laboratory                                                        
\\ Jakob Blomer          
\\ Carl Boettiger        &  UCSC/ropensci                                                                        
\\ Chris Bogart          &  ISR/CMU                                                                              
\\ Steven R.~Brandt      &  Louisiana State University                                                           
\\ Tom Clune             &  NASA GSFC                                                                            
\\ John W.~Cobb          
\\ Dirk Colbry           &  Michigan State University                                                            
\\ Karen Cranston        &  NESCent                                                                              
\\ Tom Crick             &  Cardiff Metropolitan University, UK                                                  
\\ Ethan Davis           &  UCAR Unidata                                                                         
\\ Robert R Downs        &  CIESIN, Columbia University                                                          
\\ Anshu Dubey           &  Lawrence Berkeley National Laboratory                                                
\\ Nicole Gasparini      &  Tulane University, New Orleans                                                       
\\ Yolanda Gil           &  Information Sciences Institute, University of Southern California                    
\\ Kurt Glaesemann       &  Pacific northwest national lab                                                       
\\ Sol Greenspan         &  National Science Foundation                                                          
\\ Ted Habermann         &  The HDF Group                                                                        
\\ Marcus D.~Hanwell     &  Kitware                                                                              
\\ Sarah Harris          &  University of Leeds                                                                  
\\ David Henty           &  EPCC, The University of Edinburgh                                                    
\\ Neil Chue Hong        &  Software Sustainability Institute \& University of Edinburgh                         
\\ James Howison         &  University of Texas                                                                  
\\ Maxime Hughes         
\\ Eric Hutton           &  University of Colorado                                                               
\\ Ray Idaszak           &  RENCI/UNC                                                                            
\\ Samin Ishtiaq         &  Microsoft Research Cambridge, UK                                                     
\\ Matt Jones            &  University of California Santa Barbara                                               
\\ Nick Jones            &  New Zealand eScience Infrastructure, University of Auckland                          
\\ Daniel S.~Katz        &  U Chicago \& Argonne                                                                 
\\ Ian Kelley            
\\ Hilmar Lapp           &  National Evolutionary Synthesis Center (NESCent) and Duke University                 
\\ Chris Lenhardt        
\\ Richard Littauer      &  MIT/University of Saarland                                                           
\\ Frank L\"{o}ffler     &  Louisiana State University                                                           
\\ Andre Luckow          &  Rutgers                                                                              
\\ Berkin Malkoc         &  Istanbul Technical University                                                        
\\ Kyle Marcus           &  University of Buffalo                                                                
\\ Bryan Marker          &  The University of Texas at Austin                                                    
\\ Suresh Marru          &  Indiana University                                                                   
\\ Robert H.~McDonald    &  Indiana University - Data to Insight Center/Libraries                                
\\ Rupert Nash           
\\ Andy Nutter-Upham     &  Whitehead Institute                                                                  
\\ Abani Patra           &  Univ @ Buffalo                                                                       
\\ Aleksandra Pawlik     &  Software Sustainability Institute                                                    
\\ Cody J.~Permann       &  Idaho National Laboratory                                                            
\\ John W.~Peterson      &  Idaho National Laboratory                                                            
\\ Benjamin Pharr        &  University of Mississippi                                                            
\\ Stephen Piccolo       &  Brigham Young University, Utah                                                       
\\ Marlon Pierce         &  Indiana University                                                                   
\\ Ray Plante            &  NCSA/University of Illinois Urbana-Champaign                                         
\\ Sushil Prasad         &  Georgia State University, Atlanta                                                    
\\ Karthik Ram           &  University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci 
\\ Mike Rilee            &  NASA/GSFC, Rilee Systems Technologies                                                
\\ Erin Robinson         &  Foundation for Earth Science                                                         
\\ Mark Schildhauer      &  NCEAS, Univ. California, Santa Barbara                                               
\\ Jory Schossau         &  Michigan State University                                                            
\\ Frank Seinstra        &  Netherlands eScience Center                                                          
\\ James Shepherd        &  Rice University                                                                      
\\ Justin Shi            
\\ Ardita Shkurti        &  University of Nottingham                                                             
\\ Alan Simpson          &  EPCC, The University of Edinburgh                                                    
\\ Carol Song            &  Purdue University                                                                    
\\ James Spencer         &  Imperial College London                                                              
\\ Tracy Teal            &  Data Carpentry                                                                       
\\ Kaitlin Thaney        &  Mozilla Science Lab                                                                  
\\ Matt Turk             &  NCSA/UIUC                                                                            
\\ Colin C.~Venters      &  University of Huddersfield                                                           
\\ Nathan Weeks          
\\ Ethan White           &  University of Florida/Utah State University                                          
\\ Nancy Wilkins-Diehr   &  SDSC                                                                                 
\\ Greg Wilson           &  Software Carpentry                                                                   
\end{longtable}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes} \label{keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Lead: Choi. Volunteers welcome---contact lead}

\todo{Live notes at \url{http://tinyurl.com/q6ew45v}.
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
Abstracts at \url{http://tinyurl.com/mnenzms}}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Kaitlin Thaney, Designing for Truth, Scale, and Sustainability}
\label{keynote1}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\todo{Slides: \url{http://tinyurl.com/las8tsq}}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Neil Chue Hong, We are the 92$\%$} 
\label{keynote2}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\todo{Slides: \url{http://tinyurl.com/pd9tmh3}}

@@

Google doc notes - 
\href{http://tinyurl.com/kqpe87z}
%https://docs.google.com/document/d/1Mivadj16_9tPrw8Nxmhp72AtNC0BEVO-f7M84FXTbSU/edit#heading=h.elaktnt2tep9

@@

Google doc notes - 
\url{http://tinyurl.com/l5t5h45}
%https://docs.google.com/document/d/1G1_U5-hkAvDKtTgT4DvUhIYvyYUY4cBBvQHJIdgADa0/edit#heading=h.v7g0nqpn1fur

@@

{\small
\begin{longtable}{ll}
   Jordan Adams          &  Tulane University
\\ Alice Allen           &  Astrophysics Source Code Library (ASCL)
\\ Gabrielle Allen       &  U Illinois
\\ Pierre-Yves Aquilanti &  TOTAL E\&P R\&T USA
\\ Wolfgang Bangerth
\\ David Bernholdt       &  Oak Ridge National Laboratory
\\ Jakob Blomer
\\ Carl Boettiger        &  UCSC/ropensci
\\ Chris Bogart          &  ISR/CMU
\\ Steven R.~Brandt      &  Louisiana State University
\\ Tom Clune             &  NASA GSFC
\\ John W.~Cobb
\\ Dirk Colbry           &  Michigan State University
\\ Karen Cranston        &  NESCent
\\ Tom Crick             &  Cardiff Metropolitan University, UK
\\ Ethan Davis           &  UCAR Unidata
\\ Robert R Downs        &  CIESIN, Columbia University
\\ Anshu Dubey           &  Lawrence Berkeley National Laboratory
\\ Nicole Gasparini      &  Tulane University, New Orleans
\\ Yolanda Gil           &  Information Sciences Institute, University of Southern California
\\ Kurt Glaesemann       &  Pacific northwest national lab
\\ Sol Greenspan         &  National Science Foundation
\\ Ted Habermann         &  The HDF Group
\\ Marcus D.~Hanwell     &  Kitware
\\ Sarah Harris          &  University of Leeds
\\ David Henty           &  EPCC, The University of Edinburgh
\\ Neil Chue Hong        &  Software Sustainability Institute \& University of Edinburgh
\\ James Howison         &  University of Texas
\\ Maxime Hughes
\\ Eric Hutton           &  University of Colorado
\\ Ray Idaszak           &  RENCI/UNC
\\ Samin Ishtiaq         &  Microsoft Research Cambridge, UK
\\ Matt Jones            &  University of California Santa Barbara
\\ Nick Jones            &  New Zealand eScience Infrastructure, University of Auckland
\\ Daniel S.~Katz        &  U Chicago \& Argonne
\\ Ian Kelley
\\ Hilmar Lapp           &  National Evolutionary Synthesis Center (NESCent) and Duke University
\\ Chris Lenhardt
\\ Richard Littauer      &  MIT/University of Saarland
\\ Frank L\"{o}ffler     &  Louisiana State University
\\ Andre Luckow          &  Rutgers
\\ Berkin Malkoc         &  Istanbul Technical University
\\ Kyle Marcus           &  University at Buffalo
\\ Bryan Marker          &  The University of Texas at Austin
\\ Suresh Marru          &  Indiana University
\\ Robert H.~McDonald    &  Indiana University - Data to Insight Center/Libraries
\\ Rupert Nash
\\ Andy Nutter-Upham     &  Whitehead Institute
\\ Abani Patra           &  University at Buffalo
\\ Aleksandra Pawlik     &  Software Sustainability Institute
\\ Cody J.~Permann       &  Idaho National Laboratory
\\ John W.~Peterson      &  Idaho National Laboratory
\\ Benjamin Pharr        &  University of Mississippi
\\ Stephen Piccolo       &  Brigham Young University, Utah
\\ Marlon Pierce         &  Indiana University
\\ Ray Plante            &  NCSA/University of Illinois Urbana-Champaign
\\ Sushil Prasad         &  Georgia State University, Atlanta
\\ Karthik Ram           &  University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
\\ Mike Rilee            &  NASA/GSFC, Rilee Systems Technologies
\\ Erin Robinson         &  Foundation for Earth Science
\\ Mark Schildhauer      &  NCEAS, Univ. California, Santa Barbara
\\ Jory Schossau         &  Michigan State University
\\ Frank Seinstra        &  Netherlands eScience Center
\\ James Shepherd        &  Rice University
\\ Justin Shi
\\ Ardita Shkurti        &  University of Nottingham
\\ Alan Simpson          &  EPCC, The University of Edinburgh
\\ Carol Song            &  Purdue University
\\ James Spencer         &  Imperial College London
\\ Tracy Teal            &  Data Carpentry
\\ Kaitlin Thaney        &  Mozilla Science Lab
\\ Matt Turk             &  NCSA/UIUC
\\ Colin C.~Venters      &  University of Huddersfield
\\ Nathan Weeks
\\ Ethan White           &  University of Florida/Utah State University
\\ Nancy Wilkins-Diehr   &  SDSC
\\ Greg Wilson           &  Software Carpentry
\end{longtable}
}
